BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications

### 2015-03-13 Paper/D5.5/D5.5.tex
Added summary.

\begin{executive}
This document describes BOAST, a metaprogramming framework to produce portable and efficient computing kernels for HPC application.
\end{executive}

>>>>

\begin{executive}
This document describes BOAST, a metaprogramming framework to produce portable
and efficient computing kernels for HPC application. BOAST offers an embedded
domain specific language to describe the kernels and their possible
optimization. BOAST also supplies a complete runtime to compile, run, benchmark,
and check the validity of the generated kernels. BOAST is being used in two
flagship HPC applications BigDFT and SPECFEM3D, to improve performance
portability of those codes.
\end{executive}
